---
title: "d06b analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(MASS)
library(plyr)
library(tidyverse)
library(lubridate)
library(memoise)
```

```{r utilities}
generic.ci_ <- function(x, n = 5000, seed = 1) {
  set.seed(seed)
  lenx = length(x)
  
  structure(
    quantile(
      replicate(n, mean(x[sample.int(lenx, replace = TRUE)])),
      c(0.025, 0.975)),
    names=c("ci.l","ci.u"))
}

generic.ci <- memoise(generic.ci_)
```

# read in data

```{r}
results.dir = "production-results/"
assignments = read_csv(paste0(results.dir, "assignments.csv")) %>%
  mutate(accept.time = ymd_hms(accept.time),
         submit.time = ymd_hms(submit.time),
         duration = difftime(submit.time, accept.time, units = "mins"))
gloss = read_csv(paste0(results.dir,"gloss.csv"))
gen = read_csv(paste0(results.dir, "generalization.csv"),
                     col_types = cols(string = col_character()))

## arrange assignments in order of time
assignments = assignments %>% arrange(accept.time)
```


```{r compute-example-correctness}
regexes = c('3a' = 'aaa+',
            'zip-code' = '[0123456789]{5}',
            'suffix-s' = '.*s\\>',
            'delimiters' = "\\[.*\\]")

example.matches = function(example, rx) {
  res = regexpr(pattern = rx, text = example)
  # make sure we match and that the *entire* string is what matches, not a substring
  res > 0 & attr(res, "match.length") == nchar(example)
}
# example.correct(example = 'aaa', rx = 'aaa+')
# example.correct(example = 'baaa', rx = 'aaa+')
# example.correct(example = 'aaaa', rx = 'aaa+')


# # testing
# View(responses %>% select(rule.id, polarity, string, correct, match) %>% arrange(rule.id, polarity))
```


# auxiliary

## how long does the task take?

```{r}
qplot(data = assignments,
      x = as.numeric(duration),
      binwidth = 1,
      color = I('white')) + 
  xlab("duration (minutes)")
```


## what did people think was a fair payment?

```{r}
fair.pay = assignments$fair_pay %>% as.numeric %>% na.omit
fair.pay = fair.pay[fair.pay < 5]
qplot(x = fair.pay,
      binwidth = 0.1,
      color = I('white')
      )
```

## how old are people?

```{r}
qplot(data = assignments,
      x = age,
      binwidth = 5)
```

they all tend to be older

## what gender are they?

```{r}
table(tolower(substr(assignments$gender, start = 1, stop = 1)))
```

## what is their programming / regex experience?

```{r}
assignments %>% select(programming.experience, regex.experience, worker.id, age, gender) %>% arrange(desc(nchar(programming.experience)))
```

## any bugs?

```{r}
assignments %>% select(bugs, worker.id) %>% arrange(desc(nchar(bugs)))
```

## how much did they enjoy the task?

```{r}
assignments %>% select(enjoy) %>% arrange(desc(nchar(enjoy)))
```

It wasn't terrible

# research


## how does correctness vary by rule.id and sequence?

```{r, fig.width = 10, fig.height = 3}
e = gen %>%
  group_by(rule.id, seq.id, worker.id) %>%
  summarise(score = mean(correct)) %>%
  group_by(rule.id, seq.id) %>%
  summarise(mean.score = mean(score),
            ci.l.score = generic.ci(score)['ci.l'],
            ci.u.score = generic.ci(score)['ci.u'],
            n = length(score)
            ) %>%
  transform(ci.l.score = ifelse(n == 1, 0, ci.l.score),
            ci.u.score = ifelse(n == 1, 1, ci.u.score)
            )
            

qplot(data = e,
      x = seq.id,
      y = mean.score,
      ymin = ci.l.score,
      ymax = ci.u.score,
      geom = 'pointrange'
      ) +
  geom_text(mapping = aes(label = paste0('n = ',n), y = 0.05), size = 3) +
  facet_grid(. ~ rule.id, scales = 'free') + ylim(0, 1) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```

(d06b) looks like the new zip-code sequence, 49bb605 (35164 +, 72755 +, 54f64 -, 256334 +, 84982 -) does pretty well, as i'd expected

## do different example sequences yield different generalization patterns?


```{r}
score.by.stim = gen %>%
  group_by(rule.id, seq.id, string) %>%
  summarise(mean.score = mean(correct),
            ci.l.score = generic.ci(correct)['ci.l'],
            ci.u.score = generic.ci(correct)['ci.u'],
            n = length(correct)
            )
```

3a:

```{r}
x.order = score.by.stim %>%
  filter(rule.id == '3a') %>%
  group_by(string) %>%
  summarise(mean.score = mean(mean.score)) %>%
  arrange(mean.score) %>%
  {.$string}

e = score.by.stim %>% filter(rule.id == '3a')
e$order = match(e$string, x.order)

ggplot(data = e) +
  geom_point(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  geom_line(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  scale_x_continuous(breaks = 1:length(x.order), labels = x.order) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))
```



zip-code:
```{r}
x.order = score.by.stim %>%
  filter(rule.id == 'zip-code') %>%
  group_by(string) %>%
  summarise(mean.score = mean(mean.score)) %>%
  arrange(mean.score) %>%
  {.$string}

e = score.by.stim %>% filter(rule.id == 'zip-code')
e$order = match(e$string, x.order)

ggplot(data = e) +
  geom_point(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  geom_line(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  scale_x_continuous(breaks = 1:length(x.order), labels = x.order) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))
```

suffix-s:

```{r}
x.order = score.by.stim %>%
  filter(rule.id == 'suffix-s') %>%
  group_by(string) %>%
  summarise(mean.score = mean(mean.score)) %>%
  arrange(mean.score) %>%
  {.$string}

e = score.by.stim %>% filter(rule.id == 'suffix-s')
e$order = match(e$string, x.order)

ggplot(data = e) +
  geom_point(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  geom_line(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  scale_x_continuous(breaks = 1:length(x.order), labels = x.order) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))
```


delimiters:

```{r}
x.order = score.by.stim %>%
  filter(rule.id == 'delimiters') %>%
  group_by(string) %>%
  summarise(mean.score = mean(mean.score)) %>%
  arrange(mean.score) %>%
  {.$string}

e = score.by.stim %>% filter(rule.id == 'delimiters')
e$order = match(e$string, x.order)

ggplot(data = e) +
  geom_point(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  geom_line(mapping = aes(x = order, y = mean.score, group = seq.id, color = seq.id)) +
  scale_x_continuous(breaks = 1:length(x.order), labels = x.order) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))
```

# analyze 10 zip-code seqs

```{r}
z10 = read.csv('gloss-zip-code-10.csv')
```

```{r}
e = z10 %>% group_by(seq.id) %>% summarise(correct = mean(regex.correct))

e.predicted = data.frame(
  seq.id = c("a33a11b", "49bb605", "b2614f0", "66584c1", "51be3ed", "1dc006e", "76aae7a", "ecba21d", "7632bef"),
  fL0_sharp = c(0.9999999999622489, 0.9999998874648376, 0.9522698261237779, 0.9999998874648376, 0.10650697891920076, 0.49999999999999994, 0.10196388929297737, 0.9999999999999876, 0.7052176369484497),
  fL0_smooth = c(6.781214805391138e-8,2.3992492648972874e-7,2.3276964198472533e-7,2.3992492648972874e-7,0.00000999987691071478,0.00000999990000099996,0.000009382535597137926,2.467592444818631e-8,9.391009335036399e-9),
  fL1_sharp = c(0.9999999997596767, 0.9999992836062245, 0.8459072229180626, 0.9999993498935654, 0.0034915493525717657, 0.07282304847596167, 0.003422839808667077, 0.9999999999999201, 0.24485084223232986),
  fL1_smooth = c(0.9999999831892926,0.9999858365892572,0.1384452484170687,0.9999858365897563,0.06438531807940046,0.2487740845126035,0.06329953761982891,0.9999999999845031,0.000889478940048822)
)

e = merge(e, e.predicted)

ggplot(data = e %>% merge(e.predicted),
      mapping = aes(y = correct)) +
  geom_point(mapping = aes(x = fL1_smooth)) +
  geom_text(mapping = aes(x = fL1_smooth + 0.05, label = seq.id), size = 2.5)
```

```{r}
ggplot(data = e %>% merge(e.predicted),
      mapping = aes(y = correct)) +
  geom_point(mapping = aes(x = fL1_sharp)) +
  geom_text(mapping = aes(x = fL1_sharp + 0.05, label = seq.id), size = 2.5)
```


```{r}
ggplot(data = e %>% merge(e.predicted),
      mapping = aes(y = correct)) +
  geom_point(mapping = aes(x = fL0_smooth)) +
  geom_text(mapping = aes(x = fL0_smooth + 0.0000001, label = seq.id), size = 2.5)
```


```{r}
ggplot(data = e %>% merge(e.predicted),
      mapping = aes(y = correct)) +
  geom_point(mapping = aes(x = fL0_sharp)) +
  geom_text(mapping = aes(x = fL0_sharp + 0.05, label = seq.id), size = 2.5)
```

