---
title: "d08a analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(MASS)
library(plyr)
library(tidyverse)
library(lubridate)
library(memoise)
```

```{r utilities}
generic.ci_ <- function(x, n = 5000, seed = 1) {
  set.seed(seed)
  lenx = length(x)
  
  structure(
    quantile(
      replicate(n, mean(x[sample.int(lenx, replace = TRUE)])),
      c(0.025, 0.975)),
    names=c("ci.l","ci.u"))
}

generic.ci <- memoise(generic.ci_)
```

# read in data

```{r}
results.dir = "sandbox-results/"
assignments = read_csv(paste0(results.dir, "assignments.csv")) %>%
  mutate(accept.time = ymd_hms(accept.time),
         submit.time = ymd_hms(submit.time),
         duration = difftime(submit.time, accept.time, units = "mins"))
gloss = read_csv(paste0(results.dir,"gloss.csv"))

## arrange assignments in order of time
assignments = assignments %>% arrange(accept.time)
```




# auxiliary

## how long does the task take?

```{r}
qplot(data = assignments,
      x = as.numeric(duration),
      binwidth = 1,
      color = I('white')) + 
  xlab("duration (minutes)")
```


## what did people think was a fair payment?

```{r}
fair.pay = assignments$fair_pay %>% as.numeric %>% na.omit
fair.pay = fair.pay[fair.pay < 5]
qplot(x = fair.pay,
      binwidth = 0.1,
      color = I('white')
      )
```

## how old are people?

```{r}
qplot(data = assignments,
      x = age,
      binwidth = 5)
```

they all tend to be older

## what gender are they?

```{r}
table(tolower(substr(assignments$gender, start = 1, stop = 1)))
```

## what is their programming / regex experience?

```{r}
assignments %>% select(programming.experience, regex.experience, worker.id, age, gender) %>% arrange(desc(nchar(programming.experience)))
```

## any bugs?

```{r}
assignments %>% select(bugs, worker.id) %>% arrange(desc(nchar(bugs)))
```

## how much did they enjoy the task?

```{r}
assignments %>% select(enjoy) %>% arrange(desc(nchar(enjoy)))
```

Better than average
some people were frustrated by the inductive nature of the task and the lack of feedback

# research


## analyze gloss correctness


```{r, fig.width = 11, fig.height = 3}
e.agg = gloss %>% group_by(rule.id, seq.id) %>% summarise(correct = mean(gloss.correct))

qplot(data = e.agg,
      facets = . ~ rule.id,
      x = seq.id,
      y = correct) + xlab("fraction of correct glosses for a sequence")
```
