---
title: "d08a analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(MASS)
library(plyr)
library(tidyverse)
library(lubridate)
library(memoise)
library(gridExtra)
```

```{r utilities}
generic.ci_ <- function(x, n = 5000, seed = 1) {
  set.seed(seed)
  lenx = length(x)
  
  structure(
    quantile(
      replicate(n, mean(x[sample.int(lenx, replace = TRUE)])),
      c(0.025, 0.975)),
    names=c("ci.l","ci.u"))
}

generic.ci <- memoise(generic.ci_)
```

# read in data

```{r}
results.dir = "production-results/"
assignments = read_csv(paste0(results.dir, "assignments.csv")) %>%
  mutate(accept.time = ymd_hms(accept.time),
         submit.time = ymd_hms(submit.time),
         duration = difftime(submit.time, accept.time, units = "mins"))
gloss = read_csv(paste0(results.dir,"gloss.csv")) %>%
  transform(exs = gsub("‖","\n", exs))

## arrange assignments in order of time
assignments = assignments %>% arrange(accept.time)
```

```{r}
corpora = 
```



# auxiliary

## how long does the task take?

```{r}
qplot(data = assignments,
      x = as.numeric(duration),
      binwidth = 1,
      color = I('white')) + 
  xlab("duration (minutes)")
```


## what did people think was a fair payment?

```{r}
fair.pay = assignments$fair_pay %>% as.numeric %>% na.omit
fair.pay = fair.pay[fair.pay < 5]
qplot(x = fair.pay,
      binwidth = 0.1,
      color = I('white')
      )
```

## how old are people?

```{r}
qplot(data = assignments,
      x = age,
      binwidth = 5)
```

they all tend to be older

## what gender are they?

```{r}
table(tolower(substr(assignments$gender, start = 1, stop = 1)))
```

## what is their programming / regex experience?

```{r}
assignments %>% select(programming.experience, regex.experience, worker.id, age, gender) %>% arrange(desc(nchar(programming.experience)))
```

## any bugs?

```{r}
assignments %>% select(bugs, worker.id) %>% arrange(desc(nchar(bugs)))
```

## how much did they enjoy the task?

```{r}
assignments %>% select(enjoy) %>% arrange(desc(nchar(enjoy)))
```

Better than average
some people were frustrated by the inductive nature of the task and the lack of feedback

# research


## analyze gloss correctness


```{r, fig.width = 11, fig.height = 5}
e.agg = gloss %>% group_by(rule.id, seq.id, exs) %>% summarise(correct = mean(gloss.correct), n = n())

qplot(data = e.agg,
      x = exs,
      y = correct) + 
  geom_text(mapping = aes(y = 0.1, label = n)) +
  facet_grid(. ~ rule.id, scales = 'free') +
  theme(axis.text.x = element_text(angle = 0)) +
  xlab("fraction of correct glosses for a sequence")
```

hmm, some surprises:
- suffix-s: the beads cats sequence i thought would be good. but there's like no variation in performance here.
- zip-code: the longest sequence (48751) doesn't do super well either.

hmm, i wonder if these are predicted by the model?

### what are the responses that people gave for various sequences?

```{r, fig.width = 11, fig.height = 8}
e.agg = gloss %>% group_by(rule.id, seq.id, exs, gloss.id, gloss) %>% summarise(n = n()) %>%
  transform(exs = paste0("(sequence ", seq.id, ")\n",
                         gsub('(.{1,40})(\\s|$)', '\\1\n', gsub('\n', ' | ', gsub('"', "", exs)))))

p1 = ggplot(data = e.agg %>% filter(rule.id == '3a')) +
  facet_grid(. ~ exs) +
  geom_bar(mapping = aes(x = gloss.id, y = n), stat = 'identity', position = 'dodge') +
  theme(strip.text.x = element_text(size = 12))

p2 = ggplot(data = e.agg %>% filter(rule.id == 'zip-code')) +
  facet_grid(. ~ exs) +
  geom_bar(mapping = aes(x = gloss.id, y = n), stat = 'identity', position = 'dodge') +
  theme(strip.text.x = element_text(size = 12))


p3 =  ggplot(data = e.agg %>% filter(rule.id == 'suffix-s')) +
  facet_grid(. ~ exs) +
  geom_bar(mapping = aes(x = gloss.id, y = n), stat = 'identity', position = 'dodge') + 
  theme(strip.text.x = element_text(size = 12))

grid.arrange(p1,p2,p3)
```

i can fit the zip-code results using L0 with a sharp likelihood.


examine model fits for L1 smooth:

```{r}
fits = fromJSON("../../../induction/L1-smooth-grid.json")
```

```{r, fig.width = 11, fig.height = 3}
qplot(data = fits,
      facets = . ~ outlierLP,
      x = listenerAlpha,
      y = teacherAlpha,
      label = round(LL),
      fill = LL,
      geom = 'tile',
      color = I('white')
      )  + geom_text(mapping = aes(label = round(LL,0)), color = 'white') + theme_classic()
```

outlierLP doesn't matter much and there best fits hug the x and y axes:

```{r, fig.width = 11, fig.height = 3}
qplot(data = fits %>% filter(LL > -400),
      facets = . ~ outlierLP,
      x = listenerAlpha,
      y = teacherAlpha,
      label = round(LL),
      fill = LL,
      geom = 'tile',
      color = I('white')
      ) + geom_text(mapping = aes(label = round(LL,0)), color = 'white') + theme_classic()
```

listenerAlpha = 0 does a good job but that has terrible implications -- just says that people are guessing.
the fact that the best teacherAlpha value is 0 is also bad, suggests that people expect teachers to say anything whatsoever.

(though i did a hack to do gradient descent in webppl and you can get -269ish )

fits for L1 sharp:


```{r}
fits = fromJSON("../../../induction/L1-sharp-grid.json")
```


```{r, fig.width = 11, fig.height = 3}
qplot(data = fits,
      facets = . ~ outlierLP,
      x = listenerAlpha,
      y = teacherAlpha,
      fill = LL,
      geom = 'tile',
      color = I('white')
      ) + geom_text(mapping = aes(label = round(LL,0)), color = 'white') + theme_classic()
```

similar pattern although likelihoods are better
(though i did a hack to do gradient descent in webppl and you can get -269ish )

L0 sharp:

```{r}
fits = fromJSON("../../../induction/L0-sharp-grid.json")

qplot(data = fits,
      x = listenerAlpha,
      y = outlierLP,
      fill = LL,
      geom = 'tile',
      color = I('white')
      ) + geom_text(mapping = aes(label = round(LL,0)), color = 'white') + theme_classic()
```

yeah, this looks better than L1


L1 smooth:
```{r}
fits = fromJSON("../../../induction/L0-smooth-grid.json")

qplot(data = fits,
      x = listenerAlpha,
      y = outlierLP,
      fill = LL,
      geom = 'tile',
      color = I('white')
      ) + geom_text(mapping = aes(label = round(LL,0)), color = 'white') + theme_classic()
```


yeah, this is not the behavior of a good model

